Influence of Connectivity on Dung Beetle Communities

### 2025-06-06 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
pepo

To test for the effects of connectivity on  abundance, species richness, and species diversity [we compared the values of the Hill Shannon and Simpson indexes in the different patch types and matrix]. For abundance and richness we used generalized linear mixed models (i.e., GLMM) fitted to a poisson distribution. We looked at [compared...looked at sounds squishy. try to use more active verbs like compared, quantified, assessed, etc.] (1) the overall species richness and (2) the abundance of the top 6 most common species in each patch type. We included the identity of the sampling block as a random effects. To model our diversity metrics we took a similar approach, but this time using GLMMs with a Gaussian distribution. All models were fit using `lme4` package.  Prior to conducting our modeling we used _qqplots_ (`DARMa` package) to evaluate the the suitability of our data.

>>>>

To test for the effects of connectivity on  abundance, species richness, and species diversity [we compared the values of the Hill Shannon and Simpson indexes in the different patch types and matrix]. For abundance and richness we used generalized linear mixed models (i.e., GLMM) fitted to a poisson distribution. Compared (1) the overall species richness and (2) the abundance of the top 6 most common species in each patch type. We included the identity of the sampling block as a random effects. To model our diversity metrics we took a similar approach, but this time using GLMMs with a Gaussian distribution. All models were fit using `lme4` package.  Prior to conducting our modeling we used _qqplots_ (`DARMa` package) to evaluate the the suitability of our data.
